%!TEX root = ../SkousenLyonCookbook.tex

\begin{recipe}
    [
      preparationtime,
      bakingtime={15 min},
      bakingtemperature={350 \degf},
      portion,
      calory,
      source = Shannen Lyon
    ]
    % Recipe title
    {Chicken Pot Pie}
    \index{chicken}
    \index{potatoes}

    \graph
    {% pictures I will help you figure out how to put them in here. Just ask me.
        small,
        big
    }

    \ingredients
    {
      2-3  & chicken breasts\\
      1 can & chicken broth\\
      1 lb. & chopped carrots\\
      3-4 large & potatoes, cubed\\
      1 sm. & bag frozen peas\\
      1 pt. & half and half\\
      1 cube & butter\\
      2 c. & flour\\
      2-3 & bay leaves\\
       & sage seasoning\\
       & salt and pepper\\
       12-4 & biscuits
    }

    \preparation
    {
      \step In a pot, boil the chicken breasts, then set aside. Save the water.
      \step In a large pot, pour in chicken broth. Add chopped carrots and potatoes and pour in the chicken water until the potatoes and carrots are covered.
      \step Add the bay leaves. Add salt, pepper, and sage to taste.
      \step Boil the veggies until soft then add the peas and half and half.
      \step Chop or shred the chicken and add to the vegetables. Continue to cook on low heat
      \step In a separate pan, melt the butter completely, add the flour to melted butter and stir until flour is dissolved (This makes the filling creamy). Add this mixture to the chicken and veggies.
      \step Stir this new mix until the butter and flour have completely mixed (melted) with the chicken mix. You will notice it start to thicken.
      \step Pour this into a casserole dish and bake at 350 for 15 minutes.
    }

    % \hint{See the biscuits recipe if you need help making the biscuits!}
\end{recipe}
\newpage
